---
title: 'Taboo Transactions'
subtitle: 'Analysis'
author: "Dean Baltiansky"
output: pdf_document
---

```{r setup, include=FALSE}
#load packages
library(lmerTest)
library(lsr)
library(psych)
library(interactions)
library(jtools)
library(gridExtra)
library(see)
library(kableExtra)
library(rstatix)
library(apa)
library(apaTables)
library(papaja)
library(extrafont)
loadfonts()
library(tidyverse)

#read in preprocessed data frames
df_s1a <- read.csv("~/Google Drive/My Drive/taboo transactions/OSF materials/manuscript/data/df_s1a.csv")
df_s1b <- read.csv("~/Google Drive/My Drive/taboo transactions/OSF materials/manuscript/data/df_s1b.csv")
df_s2 <- read.csv("~/Google Drive/My Drive/taboo transactions/OSF materials/manuscript/data/df_s2.csv")

```

# Demographics

## Study 1A

### N

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s1a %>% 
  summarise(N = n()) %>% 
  kbl(booktabs = T)
```

### Gender

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s1a %>% 
  group_by(gender) %>% 
  summarise(N = n()) %>% 
  mutate(perc = 100*round(N/sum(N),4)) %>% 
  ungroup() %>% 
  mutate(gender = replace_na(gender,"other")) %>% 
  kbl(booktabs = T)
```

### Race

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s1a %>% 
  group_by(race) %>% 
  summarise(N = n()) %>% 
  mutate(perc = 100*round(N/sum(N),4)) %>% 
  ungroup() %>% 
  mutate(race = replace_na(race,"other")) %>% 
  kbl(booktabs = T)
```

### Education

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s1a %>% 
  mutate(edu = factor(edu,c("GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD"))) %>% 
  group_by(edu) %>% 
  summarise(N = n()) %>% 
  mutate(perc = 100*round(N/sum(N),4)) %>% 
  ungroup() %>% 
  filter(!is.na(edu)) %>% 
  kbl(booktabs = T)
```

### Income

```{r,fig.align='left',fig.dim=c(5,2),echo=F,message=F}
df_s1a %>% 
  mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000"))) %>% 
  filter(!is.na(income)) %>% 
  ggplot(aes(x = income)) +
  geom_bar() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold",
                                   angle = 320),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

## Study 1B

### N

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s1b %>% 
  summarise(N = n()) %>% 
  kbl(booktabs = T)
```

### Gender

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s1b %>% 
  group_by(gender) %>% 
  summarise(N = n()) %>% 
  mutate(perc = 100*round(N/sum(N),4)) %>% 
  ungroup() %>% 
  mutate(gender = replace_na(gender,"other")) %>% 
  kbl(booktabs = T)
```

### Race

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s1b %>% 
  group_by(race) %>% 
  summarise(N = n()) %>% 
  mutate(perc = 100*round(N/sum(N),4)) %>% 
  ungroup() %>% 
  mutate(race = replace_na(race,"other")) %>% 
  kbl(booktabs = T)
```

### Age

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s1b %>% 
  summarise(age_m = mean(age),
            age_sd = sd(age)) %>% 
  kbl(booktabs = T)
```


### Education

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s1b %>% 
  mutate(edu = factor(edu,c("GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD"))) %>% 
  group_by(edu) %>% 
  summarise(N = n()) %>% 
  mutate(perc = 100*round(N/sum(N),4)) %>% 
  ungroup() %>% 
  filter(!is.na(edu)) %>% 
  kbl(booktabs = T)
```

### Income

```{r,fig.align='left',fig.dim=c(5,2),echo=F,message=F}
df_s1b %>% 
  mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000"))) %>% 
  filter(!is.na(income)) %>% 
  ggplot(aes(x = income)) +
  geom_bar() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold",
                                   angle = 320),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

## Study 2

### N

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s2 %>% 
  summarise(N = n()) %>% 
  kbl(booktabs = T)
```

### Gender

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s2 %>% 
  group_by(gender) %>% 
  summarise(N = n()) %>% 
  mutate(perc = 100*round(N/sum(N),4)) %>% 
  ungroup() %>% 
  mutate(gender = replace_na(gender,"other")) %>% 
  kbl(booktabs = T)
```

### Race

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s2 %>% 
  group_by(race) %>% 
  summarise(N = n()) %>% 
  mutate(perc = 100*round(N/sum(N),4)) %>% 
  ungroup() %>% 
  mutate(race = replace_na(race,"other")) %>% 
  kbl(booktabs = T)
```

### Education

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s2 %>% 
  mutate(edu = factor(edu,c("GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD"))) %>% 
  group_by(edu) %>% 
  summarise(N = n()) %>% 
  mutate(perc = 100*round(N/sum(N),4)) %>% 
  ungroup() %>% 
  filter(!is.na(edu)) %>% 
  kbl(booktabs = T)
```

### Income

```{r,fig.align='left',fig.dim=c(5,2),echo=F,message=F}
df_s2 %>% 
  mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000"))) %>% 
  filter(!is.na(income)) %>% 
  ggplot(aes(x = income)) +
  geom_bar() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold",
                                   angle = 320),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

# Cronbach's alpha

## Study 1A

### Buyers

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_alpha <- df_s1a %>% 
  select(PID,cond,ends_with("_benefit_A")) %>% 
  mutate(benefit_A_1 = ifelse(cond == 1,phone_benefit_A,noisy_benefit_A),
         benefit_A_2 = ifelse(cond == 1,kdny_benefit_A,car_benefit_A),
         benefit_A_3 = ifelse(cond == 1,chem_benefit_A,furn_benefit_A),
         benefit_A_4 = ifelse(cond == 1,prod_benefit_A,bugs_benefit_A),
         benefit_A_5 = ifelse(cond == 1,appt_benefit_A,cncrt_benefit_A)) %>% 
  select(benefit_A_1:benefit_A_5) %>% 
  psych::alpha()

for_alpha$total %>% 
  kbl(booktabs = T)
```

### Sellers

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_alpha <- df_s1a %>% 
  select(PID,cond,ends_with("_benefit_B")) %>% 
  mutate(benefit_B_1 = ifelse(cond == 1,phone_benefit_B,noisy_benefit_B),
         benefit_B_2 = ifelse(cond == 1,kdny_benefit_B,car_benefit_B),
         benefit_B_3 = ifelse(cond == 1,chem_benefit_B,furn_benefit_B),
         benefit_B_4 = ifelse(cond == 1,prod_benefit_B,bugs_benefit_B),
         benefit_B_5 = ifelse(cond == 1,appt_benefit_B,cncrt_benefit_B)) %>% 
  select(benefit_B_1:benefit_B_5) %>% 
  psych::alpha()

for_alpha$total %>% 
  kbl(booktabs = T)
```

## Study 1B

### Buyers

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_alpha <- df_s1b %>% 
  select(PID,cond,ends_with("_benefit_A")) %>% 
  mutate(benefit_A_1 = ifelse(cond == 1,phone_benefit_A,noisy_benefit_A),
         benefit_A_2 = ifelse(cond == 1,kdny_benefit_A,car_benefit_A),
         benefit_A_3 = ifelse(cond == 1,chem_benefit_A,furn_benefit_A),
         benefit_A_4 = ifelse(cond == 1,prod_benefit_A,bugs_benefit_A),
         benefit_A_5 = ifelse(cond == 1,appt_benefit_A,cncrt_benefit_A)) %>% 
  select(benefit_A_1:benefit_A_5) %>% 
  psych::alpha()

for_alpha$total %>% 
  kbl(booktabs = T)
```

### Sellers

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_alpha <- df_s1b %>% 
  select(PID,cond,ends_with("_benefit_B")) %>% 
  mutate(benefit_B_1 = ifelse(cond == 1,phone_benefit_B,noisy_benefit_B),
         benefit_B_2 = ifelse(cond == 1,kdny_benefit_B,car_benefit_B),
         benefit_B_3 = ifelse(cond == 1,chem_benefit_B,furn_benefit_B),
         benefit_B_4 = ifelse(cond == 1,prod_benefit_B,bugs_benefit_B),
         benefit_B_5 = ifelse(cond == 1,appt_benefit_B,cncrt_benefit_B)) %>% 
  select(benefit_B_1:benefit_B_5) %>% 
  psych::alpha()

for_alpha$total %>% 
  kbl(booktabs = T)
```

## Study 2

### Buyers Short-term

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_alpha <- df_s2 %>% 
  select(ends_with("_short_A")) %>% 
  select(-benefit_short_A) %>% 
  psych::alpha()

for_alpha$total %>% 
  kbl(booktabs = T)
```

### Buyers Long-term

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_alpha <- df_s2 %>% 
  select(ends_with("_long_A")) %>% 
  select(-benefit_long_A) %>% 
  psych::alpha()

for_alpha$total %>% 
  kbl(booktabs = T)
```

### Sellers Short-term

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_alpha <- df_s2 %>% 
  select(ends_with("_short_B")) %>% 
  select(-benefit_short_B) %>% 
  psych::alpha()

for_alpha$total %>% 
  kbl(booktabs = T)
```

### Sellers Long-term

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_alpha <- df_s2 %>% 
  select(ends_with("_long_B")) %>% 
  select(-benefit_long_B) %>% 
  psych::alpha()

for_alpha$total %>% 
  kbl(booktabs = T)
```

# Analysis

## Study 1A

### Descriptives

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s1a %>% 
  mutate(cond = ifelse(cond == 1,"Taboo Transactioins","Standard Transactions")) %>% 
  group_by(cond) %>% 
  summarise(benefit_A_m = mean(benefit_A),
            benefit_A_sd = sd(benefit_A),
            benefit_B_m = mean(benefit_B),
            benefit_B_sd = sd(benefit_B)) %>% 
  kbl(booktabs = T)
```
### Two-way Repeated Measures ANOVA

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_m1 <- df_s1a %>% 
  select(PID:benefit_B) %>% 
  mutate(cond = ifelse(cond == 1,"taboo","standard")) %>% 
  rename(buyer = benefit_A,
         seller = benefit_B) %>% 
  pivot_longer(-c(PID,cond),
               names_to = "person",
               values_to = "benefit")

m1 <- anova_test(
  data = for_m1, dv = benefit, wid = PID,
  within = person,
  between = cond
  )

get_anova_table(m1) %>% 
  kbl(booktabs = T)
```

### Bonferrone-corrected post-hoc comparisons: Party

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m1a <- for_m1 %>%
  group_by(person) %>%
  anova_test(dv = benefit, wid = PID, between = cond) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m1a %>% 
  kbl(booktabs = T)
```

### Bonferrone-corrected post-hoc comparisons: Condition

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m1b <- for_m1 %>%
  group_by(cond) %>%
  anova_test(dv = benefit, wid = PID, within = person) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m1b %>% 
  kbl(booktabs = T)
```

### One-sample t-tests

**Buyers in Taboo Condition:** 
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_t <- for_m1 %>% 
  filter(person == "buyer") %>% 
  filter(cond == "taboo")

t_apa(apa::t_test(for_t$benefit,alternative = "greater",mu = 0),
      format = "rmarkdown")
```

**Buyers in Standard Condition:** 
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_t <- for_m1 %>% 
  filter(person == "buyer") %>% 
  filter(cond == "standard")

t_apa(apa::t_test(for_t$benefit,alternative = "greater",mu = 0),
      format = "rmarkdown")
```

**Sellers in Taboo Condition:** 
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_t <- for_m1 %>% 
  filter(person == "seller") %>% 
  filter(cond == "taboo")

t_apa(apa::t_test(for_t$benefit,alternative = "less",mu = 0),
      format = "rmarkdown")
```

**Sellers in Standard Condition:** 
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_t <- for_m1 %>% 
  filter(person == "seller") %>% 
  filter(cond == "standard")

t_apa(apa::t_test(for_t$benefit,alternative = "greater",mu = 0),
      format = "rmarkdown")
```

## Study 1B

### Descriptives

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s1b %>% 
  mutate(cond = ifelse(cond == 1,"Taboo Transactioins","Standard Transactions")) %>% 
  group_by(cond) %>% 
  summarise(benefit_A_m = mean(benefit_A),
            benefit_A_sd = sd(benefit_A),
            benefit_B_m = mean(benefit_B),
            benefit_B_sd = sd(benefit_B)) %>% 
  kbl(booktabs = T)
```
### Two-way Repeated Measures ANOVA

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_m1 <- df_s1b %>% 
  select(PID:benefit_B) %>% 
  mutate(cond = ifelse(cond == 1,"taboo","standard")) %>% 
  rename(buyer = benefit_A,
         seller = benefit_B) %>% 
  pivot_longer(-c(PID,cond),
               names_to = "person",
               values_to = "benefit")

m1 <- anova_test(
  data = for_m1, dv = benefit, wid = PID,
  within = person,
  between = cond
  )

get_anova_table(m1) %>% 
  kbl(booktabs = T)
```

### Bonferrone-corrected post-hoc comparisons: Party

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m1a <- for_m1 %>%
  group_by(person) %>%
  anova_test(dv = benefit, wid = PID, between = cond) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m1a %>% 
  kbl(booktabs = T)
```

### Bonferrone-corrected post-hoc comparisons: Condition

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m1b <- for_m1 %>%
  group_by(cond) %>%
  anova_test(dv = benefit, wid = PID, within = person) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m1b %>% 
  kbl(booktabs = T)
```

### One-sample t-tests

**Buyers in Taboo Condition:** 
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_t <- for_m1 %>% 
  filter(person == "buyer") %>% 
  filter(cond == "taboo")

t_apa(apa::t_test(for_t$benefit,alternative = "greater",mu = 0),
      format = "rmarkdown")
```

**Buyers in Standard Condition:** 
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_t <- for_m1 %>% 
  filter(person == "buyer") %>% 
  filter(cond == "standard")

t_apa(apa::t_test(for_t$benefit,alternative = "greater",mu = 0),
      format = "rmarkdown")
```

**Sellers in Taboo Condition:** 
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_t <- for_m1 %>% 
  filter(person == "seller") %>% 
  filter(cond == "taboo")

t_apa(apa::t_test(for_t$benefit,alternative = "less",mu = 0),
      format = "rmarkdown")
```

**Sellers in Standard Condition:** 
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
for_t <- for_m1 %>% 
  filter(person == "seller") %>% 
  filter(cond == "standard")

t_apa(apa::t_test(for_t$benefit,alternative = "greater",mu = 0),
      format = "rmarkdown")
```

## Study 2

### Descriptives

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s2_long <- df_s2 %>% 
  select(PID:benefit_long_B) %>% 
  pivot_longer(-PID,
               names_to = "names",
               values_to = "benefit") %>% 
  separate(names,into = c("temp","timeframe","person"),sep = "_") %>% 
  mutate(person = ifelse(person == "A","buyer","seller")) %>% 
  select(-temp)

```

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s2_long %>% 
  group_by(person,timeframe) %>% 
  summarise(benefit_m = mean(benefit),
            benefit_sd = sd(benefit)) %>% 
  kbl(booktabs = T)
```

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
df_s2 %>% 
  summarise(benefit_A_m = mean(benefit_A),
            benefit_A_sd = sd(benefit_A),
            benefit_B_m = mean(benefit_B),
            benefit_B_sd = sd(benefit_B)) %>% 
  kbl(booktabs = T)
```

### Two-way Repeated Measures ANOVA

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m1 <- anova_test(
  data = df_s2_long, dv = benefit, wid = PID,
  within = c(person,timeframe)
  )

get_anova_table(m1) %>% 
  kbl(booktabs = T)
```

### Bonferrone-corrected post-hoc comparisons: Party

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m1a <- df_s2_long %>%
  group_by(person) %>%
  anova_test(dv = benefit, wid = PID, within = timeframe) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m1a %>% 
  kbl(booktabs = T)
```

### Bonferrone-corrected post-hoc comparisons: Timeframe

```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
m1b <- df_s2_long %>%
  group_by(timeframe) %>%
  anova_test(dv = benefit, wid = PID, within = person) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

m1b %>% 
  kbl(booktabs = T)
```

### One-sample t-tests

**Buyers across timeframes:** 
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
t_apa(apa::t_test(df_s2$benefit_A,alternative = "greater",mu = 0),
      format = "rmarkdown")
```

**Sellers across timeframes:** 
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
t_apa(apa::t_test(df_s2$benefit_B,alternative = "less",mu = 0),
      format = "rmarkdown")
```

**Buyers in the short term:** 
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
t_apa(apa::t_test(df_s2$benefit_short_A,alternative = "greater",mu = 0),
      format = "rmarkdown")
```

**Buyers in the long term:** 
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
t_apa(apa::t_test(df_s2$benefit_long_A,alternative = "greater",mu = 0),
      format = "rmarkdown")
```

**Sellers in the short term:** 
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
t_apa(apa::t_test(df_s2$benefit_short_B,alternative = "less",mu = 0),
      format = "rmarkdown")
```

**Sellers in the long term:** 
```{r,results='asis',echo=FALSE,warning=FALSE,message=FALSE}
t_apa(apa::t_test(df_s2$benefit_long_B,alternative = "less",mu = 0),
      format = "rmarkdown")
```
